CF Registry Analysis

### 2024-11-12 Christine Chan/CF Registry/cf_registry_survival_analysis.qmd
fixed table labels

```{r}
tbl_merge(
  tbls = list("2003 - 2008" = t1, "2009 - 2013" = t2, "2014 - 2018" = t3)
)
ggcoef_compare(
  list("2003 - 2008" = era1, "2009 - 2013" = era2, "2014 - 2018" = era3),
  add_reference_rows = T, exponentiate = T, type = "faceted", colour = F
)
```

>>>>

```{r}
tbl_merge(
  tbls = list(t1, t2, t3),
  tab_spanner = c("2003 - 2008", "2009 - 2013", "2014 - 2018")
)
ggcoef_compare(
  list("2003 - 2008" = era1, "2009 - 2013" = era2, "2014 - 2018" = era3),
  add_reference_rows = T, exponentiate = T, type = "faceted", colour = F
)
```
